Panel Seminars

### 2022-02-03 index.Rmd
undo demo

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
---
title: "Introduction"
---
Test
The MarineOmics working group is part of the [RCN for Evolution in Changing Seas](https://rcn-ecs.github.io/), and was formed to promote **reproducible** and **robust** genomic research in nonmodel species, but especially marine and aquatic studies. Methods in next generation sequencing and bioinformatics advance at a pace that quickly render any static set of best practices obsolete. MarineOmics aims to support robust genomic research in ecology and evolution by disseminating guidelines through this dynamic, open-sourced website addressing introductory and advanced topics of population- and functional genomics.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
---
title: "Introduction"
---

The MarineOmics working group is part of the [RCN for Evolution in Changing Seas](https://rcn-ecs.github.io/), and was formed to promote **reproducible** and **robust** genomic research in nonmodel species, but especially marine and aquatic studies. Methods in next generation sequencing and bioinformatics advance at a pace that quickly render any static set of best practices obsolete. MarineOmics aims to support robust genomic research in ecology and evolution by disseminating guidelines through this dynamic, open-sourced website addressing introductory and advanced topics of population- and functional genomics.
